---
title: "Task1"
author: "Izabele Vilkinaite"
date: "2016 m. vasaris 23 d."
output: html_document
---

# [R packages](https://www.rstudio.com/products/rpackages/) 

(1) ### ggplot2

It is a plotting system for R, based on the grammar of graphics, which tries to take the good parts of base and lattice graphics and none of the bad parts. It takes care of many of the fiddly details that make plotting a hassle (like drawing legends) as well as providing a powerful model of graphics that makes it easy to produce complex multi-layered graphics.

There are many [types of plot.](http://docs.ggplot2.org/current/)  

### Examples

(1) Here's how to do that with the **qplot** function.

```{r}

library(ggplot2)
qplot(carat, price, data=diamonds, color=clarity, xlab="Carat Weight", ylab="Price", main="Price by Carat Weight")
```

(2) With the **ggplot** function

```{r}

library(ggplot2)
ggplot(economics_long, aes(date, value01, colour = variable)) + geom_line()
```

[Original material](http://ggplot2.org/)

(2) ### Shiny

Shiny is an R package that makes it easy to build interactive web applications (apps) straight from R. [More information](http://shiny.rstudio.com/)
